Inference for Numerical Data

### 2018-10-30 DATA606/Inference for Numerical Data.Rmd
Minor correction

(c) Below is part of the output associated with this test. Fill in the empty cells.

|           |    Df   | Sum Sq  | Mean Sq | F value | Pr(>F) |
|-----------|---------|---------|---------|---------|--------|
| degree    |         |         | 501.54  |         | 0.0682 |
| Residuals |         | 267,382 |         |         |        |
| Total     |**1,172**|         |         |         |        |

>>>>

(c) Below is part of the output associated with this test. Fill in the empty cells.
```{r}
mu <- c(38.67, 39.6, 41.39, 42.55, 40.85)
sd <- c(15.81, 14.97, 18.1, 13.62, 15.51)
n <- c(121, 546, 97, 253, 155)

n <- 1172
k <- 5
Prf <- 0.0682
f_value <- qf( 1 - Prf, k-1 , n-k)

# Get missing values
sum_sq <- 501.54 * (k-1)
mean_sq <- 267382 / (n-k)
total <- sum_sq + 267382
```

|           |      Df     |    Sum Sq    |    Mean Sq    |    F value     | Pr(>F) |
|-----------|-------------|--------------|---------------|----------------|--------|
| degree    |**`r k-1 ` **|**`r sum_sq`**|    501.54     | **`r f_value`**| 0.0682 |
| Residuals |**`r n-k` ** |    267,382   |**`r mean_sq`**|                |        |
| Total     |  **1,172**  |**269388.16** |               |                |        |
